### 2020-11-14 thesis/appendix_1.tex
apprendix fix
continuating

\begin{table}[h!]
\centering
\caption{Description and data sources for all variables used in the Random Forest - Cellular Automata model.}
\label{tab:variables}
\begin{tabular}{lll}
\hline
\textbf{Variable} & \textbf{Format} & \textbf{Source}  \\ 
\hline
Distance from urban land & \multirow{3}{*}{Raster} & \multirow{2}{*}{Generated from land cover data} \\ \cline{1-1}
Size of forest patch &  &  \\ \cline{1-1} \cline{3-3} 
Elevation &  & \begin{tabular}[c]{@{}l@{}}SRTM 30m from \\ Google Earth Engine \\ data library\end{tabular} \\ \hline
Population change & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Tabular data joined to vector \\ data and rasterized\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Canadian Census for \\ 1991, 2001 and 2011\end{tabular}} \\ \cline{1-1}
Income &  &  \\ \hline
Road network & Vector data (rasterized) & Adresses Québec \\ 
\hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Neighborhood rules for ST-Sim transitions.}
\label{tab:neigh_rules}
\begin{tabular}{llcc}
\hline
\textbf{Transition} & \textbf{State counted} & \textbf{Neighborhood (m)} & \textbf{Minimum Proportion} \\ \hline
Urbanization & Urban & 500 & 0.7 \\
Agricultural Expansion & Agriculture & 250 & 0.9 \\
Reforestation & Forest (any type) & 250 & 0.9 \\
Forest Internals & Forest (specific type) & 225 & 0.15 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Pixel suitability table based on forest types and age.}
\label{tab:suit_pixls}
\begin{tabular}{lccccccccc}
\cline{2-10}
 & \multicolumn{9}{c}{\textbf{Forest}} \\ \cline{2-10} 
\textbf{} & \multicolumn{3}{c}{\textbf{Deciduous}} & \multicolumn{3}{c}{\textbf{Mixt}} & \multicolumn{3}{c}{\textbf{Coniferous}} \\ \hline
\textbf{Species} & \textbf{Young} & \textbf{Medium} & \textbf{Old} & \textbf{Young} & \textbf{Medium} & \textbf{Old} & \textbf{Young} & \textbf{Medium} & \textbf{Old} \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} & 0 & 0.5 & 1 & 0 & 0.5 & 1 & 0 & 0 & 0 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} & 0 & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 1 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} & 1 & 1 & 1 & 1 & 0.5 & 1 & 0 & 0 & 0 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} & 1 & 1 & 1 & 0.5 & 0.5 & 0.5 & 1 & 1 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Resistance reclassification table for non-forest pixels.}
\label{tab:key_non_forest}
\begin{tabular}{lcccccc}
\hline
\textbf{Species} & \textbf{Urban land} & \textbf{Roads} & \textbf{Agricultural land} & \textbf{Wetlands} & \textbf{Water} & \textbf{Other} \\ \hline 
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} 	&  32 & 32 &	8    & 8 & 16 & 8\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} 	&  32 & 32 &	16  & 8 &	 16 & 8\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} 	&  32 & 32 &	8    & 8 & 32 & 8	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} 			&  32 & 32 &	8    & 2 & 8   &	 8	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} 		&  32 & 32 &	16  & 2 &	 16 & 8\\ \hline
\end{tabular}
\end{table}

\clearpage

@@

\begin{table}[h!]
\centering
\caption{Minimum patch size for suitability table of a patch in the habitat suitability analysis.}
\label{tab:patch_size}
\begin{tabular}{lc}
\hline
\textbf{Species} 																									& \textbf{Minimum patch size} (hectares) \\ \hline 
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} 	&  1		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} 	&  150		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} 	&  1		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} 			&  1		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} 		&  1200		\\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Resistance reclassification table for different forest patches types.}
\label{tab:hab_or_not}
\begin{tabular}{lccc}
\hline
\textbf{Species} & \textbf{Habitat patch} & \textbf{Habitat patch - too small} & \textbf{Non-habitat patch} \\ \hline 
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} 	&	1	&	2	&	4	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} 	&  1	&	4	&	8	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} 	&  1	&	2	&	4	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} 			&  1	&	2	&	4	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} 		&  1	&	4	&	16	\\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{SURF analysis parameters.}
\label{tab:surf}
\begin{tabular}{lc}
\hline
\hline
Parameter & Value \\ \hline
Hessian threshold & 7000 \\
Number of octaves & 1 \\
Number of octave layers & 2 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\centering
\caption{Description and data sources for all variables used in the Random Forest - Cellular Automata model.}
\label{tab:variables}
\begin{tabular}{lll}
\hline
\textbf{Variable} & \textbf{Format} & \textbf{Source}  \\ 
\hline
Distance from urban land & \multirow{3}{*}{Raster} & \multirow{2}{*}{Generated from land cover data} \\ \cline{1-1}
Size of forest patch &  &  \\ \cline{1-1} \cline{3-3} 
Elevation &  & \begin{tabular}[c]{@{}l@{}}SRTM 30m from Google \\ Earth Engine data library\end{tabular} \\ \hline
Population change & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Tabular data joined to vector \\ data and rasterized\end{tabular}} & \multirow{2}{*}{\begin{tabular}[c]{@{}l@{}}Canadian Census for \\ 1991, 2001 and 2011\end{tabular}} \\ \cline{1-1}
Income &  &  \\ \hline
Road network & Vector data (rasterized) & Adresses Québec \\ 
\hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption[Rules for the transitions in the land use change model]{Rules for the transitions in the land use change model. The transition is only allowed if the Proportion of the Pixel counted is reached in the Neighborhood.}
\label{tab:neigh_rules}
\begin{tabular}{llcc}
\hline
\textbf{Transition} & \textbf{Pixel counted} & \textbf{Neighborhood (m)} & \textbf{Minimum Proportion} \\ \hline
Urbanization & Urban & 500 & 0.7 \\
Agricultural Expansion & Agriculture & 250 & 0.9 \\
Reforestation & Forest (any type) & 250 & 0.9 \\
Forest Internals & Forest (specific type) & 225 & 0.15 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption[Rules for the suitability analysis of forest pixels]{Rules for the suitability analysis of forest pixels. For each species, forest pixels are classified into suitability values based on forest types and age.}
\label{tab:suit_pixls}
\begin{tabular}{lccccccccc}
\textbf{} & \multicolumn{3}{c}{\textbf{Deciduous}} & \multicolumn{3}{c}{\textbf{Mixed}} & \multicolumn{3}{c}{\textbf{Coniferous}} \\ \hline
\textbf{Species} & \textbf{Young} & \textbf{Medium} & \textbf{Old} & \textbf{Young} & \textbf{Medium} & \textbf{Old} & \textbf{Young} & \textbf{Medium} & \textbf{Old} \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} & 0 & 0.5 & 1 & 0 & 0.5 & 1 & 0 & 0 & 0 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} & 0 & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 1 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} & 1 & 1 & 1 & 1 & 0.5 & 1 & 0 & 0 & 0 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 \\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} & 1 & 1 & 1 & 0.5 & 0.5 & 0.5 & 1 & 1 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption[Rules for the reclassification into resistance of non-forest pixels]{Rules for the reclassification into resistance of non-forest pixels. For all species, pixels of different land uses are classified into the same resistance values.}
\label{tab:key_non_forest}
\begin{tabular}{lcccccc}
\hline
\textbf{Species} & \textbf{Urban land} & \textbf{Roads} & \textbf{Agricultural land} & \textbf{Wetlands} & \textbf{Water} & \textbf{Other} \\ \hline 
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} 	&  32 & 32 &	8    & 8 & 16 & 8\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} 	&  32 & 32 &	16  & 8 &	 16 & 8\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} 	&  32 & 32 &	8    & 8 & 32 & 8	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} 			&  32 & 32 &	8    & 2 & 8   &	 8	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} 		&  32 & 32 &	16  & 2 &	 16 & 8\\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption[Minimum patch size rules for the suitability analysis of forest patches]{Minimum patch size rules for the suitability analysis of forest patches. A patch of forest is only deemed suitable if its size is above the minimum size.}
\label{tab:patch_size}
\begin{tabular}{lc}
\hline
\textbf{Species} & \textbf{Minimum patch size} (hectares) \\ \hline 
\textit{\begin{tabular}[c]{@{}l@{}}Blarina brevicauda\end{tabular}} 	&  1		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes americana\end{tabular}} 	&  150		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon cinereus\end{tabular}} 	&  1		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana sylvatica\end{tabular}} 			&  1		\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus americanus\end{tabular}} 		&  1200		\\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption[Rules for the reclassification into resistance of forest patches]{Rules for the reclassification into resistance of forest patches. For each species, forest patches are classified into different resistance values based on whether they are considered suitable habitat, too small or non-habitat. For a patch to be considered habitat, the majority of its pixels mush have a suitability value of 1 (see table \ref{tab:suit_pixls}) and its size must be above the minimum size for the species (see table \ref{tab:patch_size}.}
\label{tab:hab_or_not}
\begin{tabular}{lccc}
\hline
\textbf{Species} & \textbf{Habitat patch} & \textbf{Habitat patch - too small} & \textbf{Non-habitat patch} \\ \hline 
\textit{\begin{tabular}[c]{@{}l@{}}Blarina \\ brevicauda\end{tabular}} 	&	1	&	2	&	4	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Martes \\ americana\end{tabular}} 	&  1	&	4	&	8	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Plethodon \\ cinereus\end{tabular}} 	&  1	&	2	&	4	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Rana \\ sylvatica\end{tabular}} 			&  1	&	2	&	4	\\ \hline
\textit{\begin{tabular}[c]{@{}l@{}}Ursus\\ americanus\end{tabular}} 		&  1	&	4	&	16	\\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption[SURF analysis parameters.]{Parameters for the SURF (Speeded-up Robust Features) analysis (Feature detection analysis). Parameters were chosen arbitrarily (see methods).}
\label{tab:surf}
\begin{tabular}{lc}
\hline
\hline
Parameter & Value \\ \hline
Hessian threshold & 7000 \\
Number of octaves & 1 \\
Number of octave layers & 2 \\ \hline
\end{tabular}
\end{table}
